\section{Literature Review}
\para{
In the context of SMEs adopting cloud computing , there is a rich body of literature identifying key drivers, challenges, and decision frameworks. Below are some important findings from previous research, and how they relate to our e‑commerce SaaS project:
}

\para{
  Jayeola \cite{jayeola2022cloud} conducted a systematic literature review of 76 studies on cloud adoption in SMEs. They found that cost savings is the most cited adoption factor, followed by perceived usefulness. Many studies use quantitative analysis methods like PLS‑SEM or interpretative approaches.
}

\para{
  Memon (2025) \cite{memon2025ccsmes} studied SMEs in Pakistan using PLS‑SEM to examine how perceived usefulness, cost efficiency, and security concerns influence cloud adoption, with organizational readiness acting as a mediator. They found that usefulness and cost efficiency positively influence adoption, whereas security concerns hinder it. This directly supports the idea that reducing cost (via SaaS) and providing clear value is crucial to getting SMEs to adopt cloud-based tools.
}

\para{
Ghimire \cite{ghimire2024sustain} researched cloud adoption in Nepalese SMEs and developed a conceptual model of sustainability in cloud usage. Factors like trust, security \& privacy, ease of use, and cost reduction were shown to strongly affect whether SMEs will continue using cloud services in the long run. This is very relevant for our project because a SaaS-based e-commerce platform must not only attract users initially but also retain them sustainably by addressing their trust and cost concerns.
}

\textbf{Implications for Our Project}
\para{Cost and Value:  our e-commerce SaaS platform must strongly communicate cost-efficiency and usability, because these are proven to drive adoption.

Trust \& Security: We should address security and privacy in the design — perhaps in our admin or tenant architecture — since sustainability depends on trust (based on Ghimire’s findings).

Ease of Use: Make the system very simple for shop owners with minimal technical skills; this supports ease-of-use as a factor.

Long-Term Adoption: Think beyond initial use — incorporate features or pricing models that encourage shop owners to stay (renew, upgrade, continue) rather than leave.

Framework Guidance: We can use a theoretical framework (like TOE or DOl) to justify why we choose certain features or design decisions.}
