\subsection{Feasibility Analysis}

\para{
The feasibility analysis examines whether the proposed e-commerce system can be developed and maintained effectively with the available resources. It is analyzed under four major aspects: technical, operational, economic, and schedule feasibility.
}

\subsubsection*{i. Technical Feasibility}

\begin{itemize}
    \item \textbf{Technology Stack Availability:} Uses ASP.NET Core, Blazor Components, and PostgreSQL, all freely available and compatible with Linux-based servers.
    \item \textbf{Developer Skillset:} The team has experience in .NET development, component-based UI, and relational databases.
    \item \textbf{System Architecture:} Modular structure allows rapid cloning and deployment for individual shops.
    \item \textbf{Hardware Requirements:} Runs on lightweight servers (2--4 GB RAM) without needing specialized hardware.
\end{itemize}

\textbf{Conclusion:} Technically feasible as all required tools and skills are available.

\subsubsection*{ii. Operational Feasibility}

\begin{itemize}
    \item \textbf{User-Friendly Interface:} Blazor-based dashboard ensures ease of use for non-technical shop owners.
    \item \textbf{Replication-Based Deployment:} Each shop receives its own instance, reducing operational complexity.
    \item \textbf{Business Adaptability:} Simple workflows support small shops with minimal digital experience.
    \item \textbf{Maintenance:} Issues and updates can be managed per-client without affecting others.
\end{itemize}

\textbf{Conclusion:} Operationally feasible with smooth usage and maintainability.

\subsubsection*{iii. Economic Feasibility}

\begin{itemize}
    \item \textbf{Low Development Cost:} Free frameworks and local development reduce overall cost.
    \item \textbf{Affordable Hosting:} Each deployment can run on low-cost cloud servers.
    \item \textbf{Reduced Infrastructure Cost:} No need for complex SaaS features like multi-tenancy or distributed systems.
    \item \textbf{Scalable Per Client:} New deployments incur minimal additional cost.
\end{itemize}

\textbf{Conclusion:} Economically feasible with low development and hosting expenses.

\subsubsection*{iv. Schedule Feasibility}

\begin{itemize}
    \item \textbf{Aligned with Academic Timeline:} Proposal (Week 3), Mid-term (Week 12), and Final Defense (end of semester).
    \item \textbf{Modular Breakdown:} Modules such as authentication, product management, and orders can be completed independently.
    \item \textbf{Realistic Time Allocation:} Each phase fits within the semester duration.
    \item \textbf{Controlled Scope:} Excludes complex SaaS features to ensure timely completion.
\end{itemize}

\textbf{Conclusion:} The project can be completed within the allotted academic schedule.

