\subsection{Requirement Analysis}

Requirement Analysis is a crucial phase in system development, where the needs of the end-users and the system are identified and documented. For this project, which focuses on a SaaS-based e-commerce platform for small shop owners, the requirements are divided into functional and non-functional requirements to ensure that the system meets the intended objectives effectively.

\textbf{Functional Requirements}

\begin{enumerate}[label=\roman*.]
  \item \textbf{User Account Management:}
  Users (shop owners) can create, update, and delete their accounts.
  Secure login and password recovery functionalities.
  
  \item \textbf{Product Management:}
  Add, update, and remove products with details such as name, description, price, and images.
  Categorization of products for easier navigation.
  
  \item \textbf{Order Management:}
  Customers can add items to the cart and place orders.
  Shop owners can view, update, and manage orders in real-time.
  
  \item \textbf{Payment Integration:}
  Secure online payment processing using multiple payment gateways.
  Generation of receipts and confirmation messages after payment.
  
  \item \textbf{Customer Interaction:}
  Customers can view product details, track orders, and provide feedback.
  Shop owners can respond to customer queries through a messaging system.
  
  \item \textbf{Reporting:}
  Automatic generation of sales reports and order summaries.
  Dashboard for quick insight into sales trends and inventory levels.

  ===================usecase diagram========================
\end{enumerate}


\textbf{Non Functional Requirements} \\
Non-functional requirements define the system’s quality attributes, ensuring reliability, usability, and performance:

\begin{enumerate}[label=\roman*.]
  \item \textbf{Performance:}
  The system should handle multiple users and orders simultaneously without delays.

\item \textbf{Scalability:}
  Ability to support a growing number of users and products as the business expands.

\item \textbf{Security:}
  Data encryption for sensitive information such as passwords and payment details.
  Regular backup of data to prevent loss.

\item \textbf{Usability:}
  Intuitive interface requiring minimal technical knowledge for shop owners.
  Responsive design for mobile and desktop users.

\item \textbf{Reliability:}
  Minimal downtime and fast recovery in case of system failures.  
\end{enumerate}
